### 2012-03-01 Krantz-v3/Chapters/chapter1/experiments.tex
fixed a few typos

 The second comparison model, HSLDA fit by performing LDA first
followed by performing inference over the hierarchically constrained label
space, does not allow
the responses to influence the topics inferred by LDA.
Combined inference has been shown to improve performance in SLDA
\cite{BleiMcAuliffe2008}. This comparison model doesn't examine the value of utilizing the structured nature 
of the label space, instead it highlights the benefit of combined inference over both the
documents and the label space.

>>>>

 The second comparison model, HSLDA fit by performing LDA first
followed by performing inference over the hierarchically constrained label
space, does not allow
the responses to influence the topics inferred by LDA.
Combined inference has been shown to improve performance in SLDA
\cite{BleiMcAuliffe2008}. This comparison model does not examine the value of utilizing the structured nature 
of the label space, instead it highlights the benefit of combined inference over both the
documents and the label space.

### 2012-03-01 Krantz-v3/Chapters/chapter1/introduction.tex
touched all kinds of good stuff... ready for adler's final contributions.
fixed a few typos

%Our work operates within the framework of topic modeling. Our approach learns
%topic models of the underlying data and labeling strategies in a joint model,
%while leveraging the hierarchical structure of the labels. 
In this chapter we focus on ``is-a'' hierarchically structured label spaces, but label spaces that are structured differently may be accommodated with relatively minor modifications. 
%
%We extend supervised latent Dirichlet
%allocation (sLDA)~\cite{BleiMcAuliffe2008} to take advantage of hierarchical
%supervision. We propose an efficient way to incorporate hierarchical
%information into the model. We hypothesize that the context of labels within
%the hierarchy provides valuable information about labeling. 
%
We show results from modeling real-world datasets in the clinical and web
retail domains. These results provide evidence that the two views (text and labels) mutually benefit  multi-label
classification.%In fact, it will be shown that the hierarchical supervised model outperforms a
That is, modeling the joint  is better than learning 
topic models and hierarchical classifiers
independently.

The remainder of this chapter is arranged as follows. Section~\ref{sec:model}
introduces hierarchically supervised LDA (HSLDA), while
Section~\ref{sec:inference} details a sampling approach to inference in HSLDA. 
Section~\ref{sec:related_work} reviews related work, and
Section~\ref{sec:experiments} shows results from applying HSLDA to health care
and web retail data.

>>>>

%Our work operates within the framework of topic modeling. Our approach learns
%topic models of the underlying data and labeling strategies in a joint model,
%while leveraging the hierarchical structure of the labels. 
In this chapter we focus on ``is-a'' hierarchically structured label spaces, but label spaces that are structured differently may be accommodated with relatively minor modifications. 
%
%We extend supervised latent Dirichlet
%allocation (sLDA)~\cite{BleiMcAuliffe2008} to take advantage of hierarchical
%supervision. We propose an efficient way to incorporate hierarchical
%information into the model. We hypothesize that the context of labels within
%the hierarchy provides valuable information about labeling. 
%
We show results from modeling real-world datasets in the clinical and web
retail domains. These results provide evidence that the two views (text and labels) mutually benefit  multi-label
classification. %In fact, it will be shown that the hierarchical supervised model outperforms a
That is, modeling the joint  is better than learning 
topic models and hierarchical classifiers
independently.

The remainder of this chapter is arranged as follows. Section~\ref{sec:model}
introduces hierarchically supervised LDA (HSLDA), while
Section~\ref{sec:inference} details a sampling approach to inference in HSLDA. 
and
Section~\ref{sec:experiments} shows results from applying HSLDA to health care
and web retail data.

### 2012-03-01 Krantz-v3/Chapters/chapter1/related_work.tex
fixed a few typos

The models that we propose in this chapter generalize the author classification example in that the label spaces we will consider are also richly structured (in addition to the input space) and the regression function we learn maps from from the input space to labels in a structured, typically hierarchical label space.  In the same way that mixed membership models are surprisingly effective, the resulting hierarchical classification models seem to be too.

>>>>

The models that we propose in this chapter generalize the author classification example in that the label spaces we will consider are also richly structured (in addition to the input space) and the regression function we learn maps from the input space to labels in a structured, typically hierarchical label space.  In the same way that mixed membership models are surprisingly effective, the resulting hierarchical classification models seem to be too.
